PM Mungbean meta-analysis

### 2021-01-18 02_Preliminary_analysis.Rmd
Parse into a flextable with named headings

```{r Full_Trial_Summary_table}
PM_MB_dat %>%
   filter(
      fungicide_ai == "control" |
         fungicide_ai == "tebuconazole" |
         fungicide_ai == "propiconazole"
   ) %>%
   mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_sev_treat = case_when(fungicide_ai != "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_control = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_treat = case_when(fungicide_ai != "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   group_by(trial_ref,
            location,
            year,
            planting_date,
            first_sign_disease) %>%
   summarise(n = n(),
             m_PM_sev_control = mean(PM_sev_control, na.rm = TRUE),
             min_PM_sev = min(PM_sev_treat, na.rm = TRUE),
             max_PM_sev = max(PM_sev_treat, na.rm = TRUE),
             m_PM_yeild_control = mean(PM_y_control, na.rm = TRUE),
             min_PM_yeild = min(PM_y_treat, na.rm = TRUE),
             max_PM_yeild = max(PM_y_treat, na.rm = TRUE),
             )%>%
   filter(min_PM_sev < 10) # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf

>>>>

```{r Full_Trial_Summary_table, warning= FALSE}
PM_MB_dat %>%
   filter(
      fungicide_ai == "control" |
         fungicide_ai == "tebuconazole" |
         fungicide_ai == "propiconazole"
   ) %>%
   mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_sev_treat = case_when(fungicide_ai != "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_control = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_treat = case_when(fungicide_ai != "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   group_by(trial_ref,
            location,
            year,
            planting_date,
            first_sign_disease) %>%
   summarise(n = n(),
             m_PM_sev_control = mean(PM_sev_control, na.rm = TRUE),
             min_PM_sev = min(PM_sev_treat, na.rm = TRUE),
             max_PM_sev = max(PM_sev_treat, na.rm = TRUE),
             m_PM_yeild_control = mean(PM_y_control, na.rm = TRUE),
             min_PM_yeild = min(PM_y_treat, na.rm = TRUE),
             max_PM_yeild = max(PM_y_treat, na.rm = TRUE),
             )%>%
   filter(min_PM_sev < 10) %>% # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
   flextable() %>%
   set_header_labels(trial_ref = "Trial code",
                     location = "Location",
                     year = "Year",
                     planting_date = "Sowing date",
                     first_sign_disease = "PM onset date",
                     n = "n treatments",
                     m_PM_sev_control = "Control mean PM severity",
                     min_PM_sev = "Minimum PM severity*",
                     max_PM_sev = "Maximum PM severity*",
                     m_PM_yeild_control = "Control mean yeild",
                     min_PM_yeild = "Minimum yeild*",
                     max_PM_yeild = "Maximum yeild*"
                     )
```
